% LaTeX Curriculum Vitae
% Author: Xovee Xu (https://xovee.cn)
% Last Update: Feb 1, 2024
% Latest Version (consider give me a star!): https://github.com/Xovee/latex-cv
% Overleaf Link: https://www.overleaf.com/latex/templates/xovees-cv-template/rrsmqwhbygcf
% Current Version: v0.96
% LICENSE: MIT


\documentclass{article}

\usepackage{yhmath}
\usepackage{bm}
\usepackage{mathrsfs,esvect}
\usepackage{tikz}


\usepackage{verbatim}
\usepackage{amssymb,amscd,amsfonts,amsbsy}
\usepackage{latexsym}
\usepackage{exscale}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{mathrsfs}
\usepackage{xcolor} % Enables the creations of colors.
\usepackage{esint} % For \fint symbol
\usepackage{amssymb} % For \lesssim symbol
\usepackage{stmaryrd}
\usepackage{cite} 
\usepackage{tikz}





%\usepackage{ctex}
\usepackage[utf8]{inputenc}
\usepackage[full]{textcomp}
\usepackage{CJKutf8}
\usepackage{newtxtext}
\usepackage[T1]{fontenc}
\usepackage{array}

\usepackage{enumitem}
\usepackage[a4paper,left=1in, right=1in, top=1.5in, bottom=1.5in]{geometry}
\usepackage{url}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath,amssymb}
\usepackage{eqparbox}
\usepackage{graphicx}

\definecolor{redo}{rgb}{0.75,0,0}
\newcommand{\sqbullet}{~\vrule height 1ex width .8ex depth -.2ex}

% package settings
\usepackage[
    pdfnewwindow=true,
    pdfauthor={MathRoc},
    pdftitle={Curriculum Vitae of MathRoc},
    pdfpagemode=UseThumbs,
]{hyperref}

\pagestyle{headings}
\markright{\textbf{}}

\setlength\parindent{2em}

\thispagestyle{empty}

% define cv section
\newcommand{\cvsection}[1]{\section*{\rmfamily#1}}
\newcommand{\cvsubsection}[1]{\subsection*{\rmfamily\hspace{1.6em}#1}}

% begin
\begin{document}

% name
\begin{center}
    \Large{
    \rmfamily
    \textbf{Xi Cen}}
\end{center}
\vspace{20pt}


\setlength{\parskip}{1pt}
\renewcommand{\arraystretch}{1.25}


% Contact Information
\noindent
\begin{tabular}{@{}ll@{}}
\bf{Address}& School of Science,\\
& China University of Mining and
Technology (Beijing),\\
& Beijing 100083, People's Republic of China\\
%\bf{Nationality}& Chinese
\end{tabular}%
\hfill
\begin{tabular}{@{}ll@{}}
\bf{Email}& \href{mailto:xicenmath@gmail.com}{xicenmath@gmail.com}\\
\bf{ResearchGate}& \href{https://www.researchgate.net/profile/Xi-Cen-8?ev=prf_overview}{\color{blue}ResearchGate--Link}\\
\bf{CV--Online}& \href{https://xicenmath.github.io/homepage/cv.pdf}
{\color{blue} https://xicenmath.github.io/homepage/cv.pdf}
\end{tabular}
\vspace{2mm}

\setlength{\parskip}{3pt}


% Personal Profile
\cvsection{Personal Profile}
\indent
My research interests mainly focus on Euclidean harmonic analysis, which can be divided into the following aspects:
\begin{itemize}
\item[(1)] The property of Multilinear Fourier integral-type operators (Fourier integral operators, pseudo-differential operators, Fourier multipliers).
\item[(2)] Sparse bounds and sharp weighted bounds of the important operators.
\item[(3)] Multilinear extrapolation theory and multilinear dyadic representation theory.
\item[(4)] The singular integral operators and maximal operators along the curve.
\item[(5)] Boundedness extended to the weighted  multi-exponent function spaces (weighted Besov spaces, weighted Triebel spaces, weighted Sobolev spaces).
\end{itemize}



% Education
\cvsection{Education}
\begin{tabular}{ll}
   % \bf{2025 - Now} & Ph.D. student in Pure Math - \href{https://www.dhu.edu.cn/}{Donghua University, Shanghai} \\& Advisor: Liangjian Hu \& Min-Jie Luo\\[.5ex]
    \bf{2025.9--now} & Master student -- {China University of Mining and Technology (Beijing)}\\
    & Advisor: \href{https://lxy.cumtb.edu.cn/info/1067/1219.htm}{\color{blue} Prof. Xinfeng Wu}\\[.5ex]
    \bf{2018.9--2022.6} & Bachelor of Science -- %\href{https://www.neu.edu.cn/} 
    {Southwest University of Science and Technology}\\
\end{tabular}


% Skills
%\cvsection{Skills}
%\begin{itemize}[label=\sqbullet~]
  %  \item Chinese (mother tongue)
    %\item English (weak in speaking)
   % \item Modern poetry (writing since 2014)
%\end{itemize}


% Contributed Talks (如果talks太多,可多次使用tabular环境,以保证不会出现大片空白)

\begin{comment}

\cvsection{Contributed Talks}
\begin{tabular}{ll}
    \bf{May 2025} & ``Asymptotics of bivariate hypergeometric functions''\\ %下引号是两个单引号
    & Haihe Postdoctoral Forum on Mathematics, Statistics \& Interdisciplinary Sciences,\\
    & Pure Mathematics\\
    & \textit{Nankai University, Tianjin}\\[.5ex]
    
    \bf{Nov 2024} & ``Asymptotics of Saran's hypergeometric function $F_K$''\\
    & 2024 Colloquium on Number Theory \& Special Functions\\
    & \textit{Donghua University, Shanghai}\\[.5ex]
    
    \bf{Sept 2024} & ``Asymptotics of hypergeometric functions''\\
    & 2024 Doctoral Academic Forum, \\
    & Nonlinear Functional Analysis and Applications\\
    & \textit{Central China Normal University, Wuhan}
\end{tabular}


% Awards and Honors
\cvsection{Awards and Honors}
\begin{tabular}{ll}
    \bf{2024} & National Scholarship for Postgraduates, \textit{China}\\
    & Outstanding Student, \textit{Donghua University}
\end{tabular}


% Collabotators
%\cvsection{Collaborators}%不公开,仅自己看
%\indent

%Petr Blaschke, \textcolor{blue}{Bujar Fejzullahu}, \textcolor{blue}{Malte Henkel}, \textcolor{blue}{Liangjian Hu}, \textcolor{blue}{Alexey Kuznetsov}, Rahul Kumar, \textcolor{blue}{Min-Jie Luo}, Kamel Mazhouda, \textcolor{blue}{Andrew Pearce-Crump}


% Remarkable Activities
\cvsection{Remarkable Activities}
\begin{itemize}[label=\sqbullet~, leftmargin=*]
    \item I co-organised the colloquium \textit{Number Theory \& Special Functions}, which was held at Donghua University on Nov. 16th, 2024.
\end{itemize}
\end{comment}


\cvsection{Professional services}	
Referee for "Journal of Function Spaces" and "AIMS Mathematics" in 2024.



% Publications
\cvsection{Publications}	
\begin{enumerate}[label=~~\bf{\arabic*.}~, leftmargin=*]
\item 
Xi Cen*,  \textbf{The multilinear Littlewood-Paley square operators and their commutators on weighted Morrey spaces},  \href{https://doi.org/10.1007/s13226-023-00406-1}{\it\textcolor{blue}{Indian J. Pure Appl. Math., 2024, 55(2): 749-775.}}
\item Xi Cen*, 
\textbf{Fractional maximal operators on weighted variable Lebesgue spaces over the spaces of homogeneous type}, \href{https://doi.org/10.1007/s13324-024-00955-6}{\it \textcolor{blue}{Anal.Math.Phys. 14, 94 (2024).}}\\
\item Xi Cen*, Qianjun He, Zichen Song, Zihan Wang, 
\textbf{New fractional type weights and the boundedness of some operators}, \href{https://doi.org/10.1007/s13324-025-01027-z}{\it \textcolor{blue}{ Anal.Math.Phys. 15, 26 (2025).}}\\ 
\item Xi Cen*, 
\textbf{New variable weighted conditions for fractional maximal operators over spaces of homogeneous type}, (Under Review).\\
%\href{https://doi.org/10.1007/s13324-024-00955-6}{\it \textcolor{blue}{Anal.Math.Phys. 14, 94 (2024).}}
\item Xi Cen*, Zichen Song,
\textbf{The multilinear fractional sparse operator theory I: pointwise domination and weighted estimate},  (Under Review)\\

\item Xi Cen*, Zichen Song,
\textbf{The multilinear fractional bounded mean oscillation operator theory I: sparse domination, sparse $T1$ theorem, off-diagonal extrapolation, quantitative weighted estimate---for generalized commutators},  (Submitted)\\
\item  Xi Cen*
\textbf{Improving sparse bounds I: dilated sparse domination for multilinear pseudo-differential operators}, (Under Review)\\
\item  Xi Cen*, 
\textbf{Sparse bounds and sharp weighted bounds for multilinear pseudo-differential operators and their commutators I}, (Under Review)\\
\item  Xi Cen*, 
\textbf{Sparse bounds and sharp weighted bounds for multilinear pseudo-differential operators and their commutators II: the multi-exponent H\"ormander class}, (Submitted)\\
\item  Xi Cen*,
\textbf{Quantitative weighted multi-exponent improvements for pseudo-differential Operators I}, (Submitted)\\
\item  Xi Cen*,
\textbf{Quantitative weighted multi-exponent improvements for pseudo-differential Operators II: the Off-diagonal estimates}, (Submitted)\\


(*--the corresponding author)



\end{enumerate}


















\begin{comment}

% Preprints
\cvsection{Preprints}
\begin{enumerate}[label=~~\bf{\arabic*.}~, leftmargin=*]
\item P.-C. Hang, L. Hu. Full asymptotic expansions of the Humbert function $\Phi_1$.
\href{https://arxiv.org/abs/2504.09280}{\color{blue}arXiv:2504.09280}

\item  P.-C. Hang, M. Henkel, M.-J. Luo. Asymptotics of the Humbert functions $\Psi_1$ and $\Psi_2$. \textit{J. Approx. Theory} (under review), \href{https://arxiv.org/abs/2501.07281}{\color{blue}arXiv:2501.07281v2}
		
\item  P.-C. Hang, L. Hu, M.-J. Luo. Complete asymptotic expansions of the Humbert function $\Psi_1$ for two large arguments. \href{https://arxiv.org/abs/2410.21985}{\color{blue}arXiv:2410.21985v3}
		
\item P.-C. Hang. Matrix analogues of some asymptotic methods for Laplace integrals. \href{https://arxiv.org/abs/2404.15573}{\color{blue}arXiv:2404.15573v2}
\end{enumerate}


% References
\cvsection{References}
\noindent
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{@{}ll@{}}
\bf{Name}& Liangjian Hu\\
\bf{Affiliation} & Donghua University\\
\bf{Position}& Professor\\
\bf{Contact}& \href{mailto:Ljhu@dhu.edu.cn}{Ljhu@dhu.edu.cn}
\end{tabular}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{@{}ll@{}}
\bf{Name}& Alexey Kuznetsov\\
\bf{Affiliation} & York University\\
\bf{Position}& Professor\\
\bf{Contact}& \href{mailto:akuznets@yorku.ca}{akuznets@yorku.ca}
\end{tabular}
\end{minipage}

\noindent
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{@{}ll@{}}
\bf{Name}& Gerg\H{o} Nemes\\
\bf{Affiliation} & Harbin Institute of Technology\\
\bf{Position}& Professor\\
\bf{Contact}& \href{mailto:g.nemes@hit.edu.cn}{g.nemes@hit.edu.cn}
\end{tabular}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{@{}ll@{}}
\bf{Name}& Weiyuan Qiu\\
\bf{Affiliation} & Fudan University\\
\bf{Position}& Professor\\
\bf{Contact}& \href{mailto:wyqiu@fudan.edu.cn}{wyqiu@fudan.edu.cn}
\end{tabular}
\end{minipage}

\vspace{2mm}

\noindent
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{@{}ll@{}}
\bf{Name}& Roderick S. C. Wong\\
\bf{Affiliation} & City University of Hong Kong\\
\bf{Position}& Emeritus Professor\\
\bf{Contact}& \href{mailto:rodscwong@gmail.com}{rodscwong@gmail.com}
\end{tabular}
\end{minipage}

\vfill

\end{comment}



\section*{\hfill\color{OliveGreen}\today}

\end{document}
